\documentclass[letterpaper,10pt,titlepage]{article}

\usepackage{graphicx}                                        

\usepackage{amssymb}                                         
\usepackage{amsmath}                                         
\usepackage{amsthm}                                          

\usepackage{alltt}                                           
\usepackage{float}
\usepackage{color}

\usepackage{url}

\usepackage{balance}
\usepackage[TABBOTCAP, tight]{subfigure}
\usepackage{enumitem}

\usepackage{pstricks, pst-node}

\usepackage{geometry}
\geometry{textheight=9in, textwidth=6.5in}

%random comment

\newcommand{\cred}[1]{{\color{red}#1}}
\newcommand{\cblue}[1]{{\color{blue}#1}}

\usepackage{hyperref}

\def\name{Joshua Villwock}

%pull in the necessary preamble matter for pygments output
\input{pygments.tex}

%% The following metadata will show up in the PDF properties
\hypersetup{
  colorlinks = true,
  urlcolor = black,
  pdfauthor = {\name},
  pdfkeywords = {cs311 ``operating systems'' files filesystem I/O},
  pdftitle = {CS 311 Project 3: UNIX File I/O},
  pdfsubject = {CS 311 Project 3},
  pdfpagemode = UseNone
}

\parindent = 0.0 in
\parskip = 0.2 in

\begin{document}
\tableofcontents

\section{Overall System Design}

\subsection{Overall Layout / theory}

The overall design of the myar aplication is fairly straightforward.  When a user runs the program, the command line parser parses it, and determins what sub-sections of the program to run.

It then opens the archive, after verifying that it begins with the proper ARMAG, and then executes the portion of the program that should deal with whatever action you wanted it to run.

\subsection{Command Line Parsing}

The parser here is fairly simple.  Initially, I was going to use getopt() but after re-reading the requirements, it appeared you wanted all the arguments first, with the files passed on the end, not right after the argument, as per standards.

\begin{itemize}
\item It starts with your first argument, (the flags, or options) and passes them into a variable to deal with later.
\item Next it takes your second argument, (the path to the archive) and stores it into a variable to deal with later.
\item Next, It will iterate through up to 7 more arguments, saving them into an array to be dealt with later.
\item Then it double checks that you have provided enough / correct arguments.  If not, it dies with an error.
\item Finally, It itterates through a list of acceptable arguments, and executes the proper portion of the program, based on whitchever one it encounters first.
\item it will check arguments in the following order:
\subitem -t
\subitem -v
\subitem -q
\subitem -x
\subitem -d
\subitem -A
\subitem errors out if nothing was found.
\end{itemize}

\subsubsection{Problems}

There were major problems with passing invalid arguments (mainly not enough arguments) and the program crashing and burning.  However, Recently, most of these cases have been trapped, and should no longer ocour.

\subsection{Listing files}

After the archive has been verified, and opened for editing / reading, all archives and read modes are initially parsed the same way.  It starts by calling getList(), whether you wanted a quicklist, or the detailed list.

getList() fetches the address of the end of the archive, initializes variables, and then begins looping through the file.  It starts imediently after ARMAG, and will read the first header, then convert the length of that header's file to an integer.

It will then lseek that far through the file, to the next file header, and read the next one.  It continues through the file in this manner, until it finally seeks to or past the end of the file.

Each time, it writes the file header into the global array of structs that stores all this data.

Once that has finished, it will call fixList() which simple iterats through the list, removing trailing slashes, invalid files, and pretying up the list.  It then falls back into whichever form of list you asked for.  The simple list pretty much just outputs what is stored in the fixed list, while the detailed list is more complex.

\subsection{Extracting Files}

Extracting files with myar is simple.  Simply use the command:
\begin{itemize}
\item myar -x <name of archive> <file to extract> [<another file to extract>]...
\end{itemize}

Internally, the commandline parser will parse through your arguments, and put all arguments after the name of the archive into an array to be used by this extraction process.

It then iterates through the list of files in the archive, and in a nested loop, iterates through the arguments you passed it.  For all matches, it will call the function to actually extract said file to its file.

\subsubsection{Caveats}

\begin{itemize}
\item I have thoughly tested with ar, and it does not seem to preserve directories, at least not absolute directories.  Hence, myar will also discard absolute directories when extracting.
\item If you specify the same file name twice, myar will sometimes extract the file twice to the same file, duplicating it twice in a single file.  Avoid this.
\item If the file you specified is not in the archive, No error message will be displayed at this time.  Simply nothing will happen.
\end{itemize}

\subsection{Adding Files}

Sadly due to time constraints, myar does not yet support inserting files into an archive, or creating a new one.

Much of the code for this is in the program, and using myar -q will invode the partially finished code, however, headers are not written properly, and YOU WILL CORRUPT YOUR ARCHIVE FILE!

\section{Work Log}

Didn't do much excedept for planning and prototyping before the 15th.

on the 16th, got general outline of code up and running.

Had -t and -v working on the 19th

Added command line support on 20th

Extraction added on 21st

Finished up on 22nd

Full outline here: \url{https://github.com/1n5aN1aC/myar/commits/master}

\section{Challenges}

I learned that strings in C are super annoying, but using some builtin methods, and making a few of your own is a lifesaver.

I had major problems with working with the struct, and I am not entirely satisfied with my solution, but the parts that are done work correctly, so...

see "what did you learn" below for more info.

\section{Questions And Answers}

\subsection{what do you think the main point of this assignment is?}

\begin{itemize}
\item Make sure we know how to use all the tools of the course (C, tex, etc.)
\item Get us used to basic system calls, and moving around inside of and reading/writing files.
\end{itemize}

\subsection{how did you ensure your solution was correct? Testing details, for instance.}

Through testing was done using archives made with UNIX's ar.  Following is a list of all the test cases Performed that I can remember:

\begin{itemize}
\item myar with no arguments
\item myar with one argument (flag) but no files specified
\item myar -t ex.a
\item myar -v ex.a
\item myar -tv ex.a   (will handle first flag only)
\item myar -t ex.a any amount of junk arguments
\item myar -v ex.a any amount of junk arguments
\item myar -t/v ex.a (where ex.a is empty) [file is corrupt]
\item myar -t/v ex.a (where ex.a has a currupted armag) [file is corrupt]
\item myar -x ex.a (no files to extract)
\item myar -x ex.a derp herp (two files not in archive)
\item myar -x ex.a thi1 (one file in archive)
\item myar -x ex.a thi1 tha2 (two files in archive)
\item myar -x ex.a thi1 derp (one file in archive, one not)
\end{itemize}

all the above command worked properly on files created with UNIXs ar.  There were several variations of options shown in this list that I did not list here, as they are very similar.

\subsection{what did you learn?}

\begin{itemize}
\item Although I previously knew some C++ this assignment has been a rude awakening on the front of c-strings, character arrays and the like
\item Overall, I would say I strongly dislike C from this couse so far.  I like my objects in Java / Python too much.
\item Although, I have mostly learned how to work with structs and character arrays in C, even though I greatly dislike it.
\item C is very frustrating to code in, and takes considerably longer than Java / Python (at least for me.)
\end{itemize}

See "Challenges" above for more info.

\end{document}
